### 2019-01-14 thesis_report/theory.tex
Updated thesis

% UNCOMMENT SO YOU CAN LINK PAPERS EASILY WITH SUBLIME TEXT
% \bibliography{report}

@@

\section{General Physics}

@@

@@

	\subsection{Majorana bound states}
		In the context of condensed matter physics, Majorana

	\subsection{Decay/Coherence length}
		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majorana's, diminishing the desired robustness of the state.

@@

	\subsection{Phase diagram}

@@

	\subsection{Thouless energy}
	\subsection{Transparency at NS interface}

>>>>

% -*- root: ./report.tex -*-

@@

\section{General Physics}
	We give a brief description of the interactions and physics present in the system under study.

@@

		\subsubsection{Thouless energy}

@@

	\subsection{Majorana bound states}
		We will give a very pragmatic description of Majorana bound states, insofar their relevance to this work.

		The Majorana state is a superposition of electrons and holes, and is its own anti-particle: exchanging electrons and holes yields the same state.
		The Majorana state carries no spin, charge, or energy, giving almost no degrees of freedom for it to interact with the environment.
		The Majorana state constitutes a single fermion, but is comprised of two Majorana's.
		In a finite, topological system, these two Majorana's are physically seperated, appearing at the edges.

		The lack of interaction, as well as the physical seperation of the state, makes it very robust against perturbations, but also difficult to detect.
		Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
		When measuring the conduction through a system with Majorana's present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.

	\subsection{Decay/Coherence length}
		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majorana's, diminishing the desired robustness of the state.
		An overlap of the Majorana's will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
		A crude estimation of the size of an individual Majorana is:
		\begin{equation}
			\xi = \hbar \frac{v_\text{F}}{\Delta}
		\end{equation}

@@

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/pientka_system}
	\caption{System overview. Source\cite{pientka_topological_2017}}
	\label{fig:pientka_system}
	\end{figure}

	The earliest devices used to create a seperated pair of Majorana's were nanowires deposited onto a slab of superconducting material.
	A relatively new proposal is that of creating Majorana's in a planar Josephson junction~\cite{pientka_topological_2017}.
	An advantage of this system is that the phase difference between the superconductors can be used as a knob to switch the system from the topological state to the trivial state. 
	In addition, the presence of the second superconductor increases the topological gap of the system due to the proximity effect.

	\subsection{Phase diagram}
	As mentioned, the superconducting phase difference plays a critical role in the physics of the device.
	The topological phase diagram, as a function of magnetic field and superconducting phase, is depicted in Fig. \ref{fig:pientka_phase_diagram}.
	Without normal reflection (perfect Andreev reflection), the diagram has a diamond-like shape.
	The system is always topological when the superconducting phase is $pi$, or when the magnetic field is tuned to $(2N-1)$ times the Thouless energy (With exception of the corners of the diamonds).

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/pientka_phase_diagram}
	\caption{Phase vs. Magnetic field. Source\cite{pientka_topological_2017}}
	\label{fig:pientka_phase_diagram}
	\end{figure}

@@

	\subsection{Transparency at NS interface}
